\textcolor{Navy}{\textsc{Convexity adjustments with a bit of Malliavin}}

### 2022-11-24 Latex/paper.tex
# new approach cms convexity

\section{Convexity Adjustment}\label{sec:CA}
In this section, we derive the convexity adjustment for different products. The advantage of using the Malliavin calculus is that it allows us to derive a general representation formula for the convexity adjustment. Since the convexity adjustment is derived for the Cheyette model, it can be applied to all included models, such as the Hull-White model.

@@

dW^{\mathbb{Q}^{t_2}} = dW^{\mathbb{Q}} + \nu(t,T_2) dt. 

@@

We suppose, that we have a flow in $T_a < T_p < T_b$ with value $S_{a,b}(T_a)$. Then, the present value of this flow
\begin{align}\label{cms_expedted_value}
P_{ois}(0,T_a)\mathbb{E}^{\mathbb{Q}^{T_{a}}}\left(S_{a,b}(T_a) P_{ois}(T_a,T_p) \right) &= 01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) \frac{P_{ois}(T_a,T_p)}{01(T_a,T_a,T_b) }\right) \nonumber \\
&= 01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) M(T_a,T_p)\right)
\end{align}
where $M(t, T_p)= \frac{P_{ois}(t,T_p) }{01(t,T_a,T_b)} $. In order to reduce the complexity to explain the movement od the forward curve, it is a common pratice to asumme that
\begin{equation*}
M(t) = f(S^{ois}_{a,b}(t))
\end{equation*}
where $f(\cdot)$ is known as mapping function. There is a extensive literature how to define this function (see Piterbarg Volume III), in later we will see some particular examples for this mapping function. Under the last assumption and applying Clark-Ocone to $f(S_{a,b}(t))$ we get
\begin{align*}
f(S^{ois}_{a,b}(T_a)) &= \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(f(S^{ois}_{a,b}(T_a)\right) + \int_{0}^{T_a} \mathbb{E}_s^{01(a,b)}\left( D_s (f(S^{ois}_{a,b}(T_a)) \right) dW^{01(a,b)}_{s} \\
&= \frac{P_{ois}(0,T_p) }{01(0,T_a,T_b)} + \int_{0}^{T_a} \mathbb{E}_s^{01(a,b)}\left(f^{\prime}(S^{ois}_{a,b}(T_a) \partial_{x}S^{ois}_{a,b}(T_a) D_s x_{T_a} \right) dW^{01(a,b)}_{s}. 
\end{align*}
Therefore, we can define the convexity adjustment for a CMS the next way
\begin{align*}
&CA_{CMS}(T_a,T_b)  \\
=&01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) \int_{0}^{T_a} \mathbb{E}_s^{01(a,b)}\left( f^{\prime}(S^{ois}_{a,b}(T_a)) \partial_{x}S^{ois}_{a,b}(T_a) D_s x_{T_a} \right) dW^{01(a,b)}_{s} \right)
\end{align*}
Now if we use again the Clark-Ocone representation, but in this case for $S_{a,b}(T_a)$ we get that
\begin{align*}
CA_{CMS}(T_a,T_b) &\approx 01(0,T_a,T_b)  f^{\prime}(S^{ois}_{a,b}(0)) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) \left( S^{ois}_{a,b}(T_a) - S^{ois}_{a,b}(0)\right)\right) \\
&= 01(0,T_a,T_b)  f^{\prime}(S^{ois}_{a,b}(0)) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S^{ois}_{a,b}(T_a)S_{a,b}(T_a) -  S_{a,b}(0) S^{ois}_{a,b}(0)\right)
\end{align*}
Where we have used that $S_{a,b}(t)$ and $S^{ois}_{a,b}(T_a)$ are $01(a,b)$-martingale. Now, if we use Itô formula to $S^{ois}_{a,b}(t)$ and $S_{a,b}(t)$ we have that
\begin{align*}
dS^{ois}_{a,b}(t,x_t,y_t) &= \partial_{x}S^{ois}_{a,b}(t,x_t,y_t)\eta(t,x_t,y_t)dW^{01(a,b)}  \\
dS_{a,b}(t,x_t,y_t) &= \partial_{x}S_{a,b}(t,x_t,y_t)\eta(t,x_t,y_t)dW^{01(a,b)} 
\end{align*}
with initial condition $S^{ois}_{a,b}(0)$ and $S_{a,b}(0)$ respectivaly. Then 
\begin{align*}
\mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S^{ois}_{a,b}(T_a)S_{a,b}(T_a) \right) &= \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(\int_0^{T_a} \partial_{x}S_{a,b}(u,x_u,y_u) \partial_{x}S^{ois}_{a,b}(u,x_u,y_u)  \eta^{2}(u,x_u,y_u)
du \right)  + S_{a,b}(0) S^{ois}_{a,b}(0) \\
&\approx  \partial_{x}S_{a,b}(0,\bar{x}_0, \bar{y}({T_a}) \partial_{x}S^{ois}_{a,b}(0,\bar{x}_0, \bar{y}({T_a}))\int_0^{T_a} \eta^{2}(u,\bar{x}_0, \bar{y}({T_a})) du \\
&+ S_{a,b}(0) S^{ois}_{a,b}(0).
\end{align*}

Then, we can approximate $CA_{CMS}(T_a,T_b)$ the next way

\fboxsep1em
\fbox{\parbox{430pt}
{
\begin{align}\label{cms_adjustment}
&CA_{CMS}(T_a,T_b)  \\
&\approx  01(0,T_a,T_b)  f^{\prime}(S^{ois}_{a,b}(0)) \nonumber \\
&\cdot \partial_{x}S_{a,b}(0,\bar{x}_0, \bar{y}({T_a}) \partial_{x}S^{ois}_{a,b}(0,\bar{x}_0, \bar{y}({T_a}))\int_0^{T_a} \eta^{2}(u,\bar{x}_0, \bar{y}({T_a})) du \nonumber
\end{align}
}}

\begin{example}
In ghe case of a Hull-White model, we showed in the example  (\ref{example_convexity_hw_ois}) that 
$$
\eta(t,x_t, y_t) = \sigma\exp(-kt)
$$
\end{example}
Therefore (\ref{cms_adjustment}) is reduced to
\begin{equation}\label{hullwhite_cms_convexity}
01(0,T_a,T_b)  f^{\prime}(S^{ois}_{a,b}(T_a)) \partial_{x}S_{a,b}(0,\bar{x}_0, \bar{y}({T_a}) \partial_{x}S^{ois}_{a,b}(0,\bar{x}_0, \bar{y}({T_a}) \frac{ \sigma^2(1-\exp(-2kT_a))}{2k} 
\end{equation}
A common practice in market, it is suppose that $f(x)=\alpha x + \beta$ (TSR model). We must to impose two equations in order to get $\alpha$ and $\beta$. The first equation follows straightforward from the definition of $M(t,T_p)$. Since, $M(t,T_p)$ is a $01(a,b)-$martingale we must have that
\begin{equation*}
\mathbb{E}^{01(a,b)}\left(\alpha S^{ois}_{a,b}(T_a) + \beta \right) = \frac{P_{ois}(0,T_p)}{01(0,T_a,T_b)}.
\end{equation*}
Therefore
\begin{equation*}
\beta = \frac{P_{ois}(0,T_p)}{01(0,T_a,T_b,x_0,y_0)} - \alpha S^{ois}_{a,b}(0,x_0,y_0).
\end{equation*}
Under a separable HJM dynamic we must have that
\begin{equation*}
\alpha \partial_{x} S^{ois}_{a,b}(0) = - M(0,T_p)\left(G(T_a,T_p)+\frac{\partial_x 01(0,T_a,T_b)}{01(0,T_a,T_b)}\right).
\end{equation*}
Then
\begin{equation*}
\alpha = -\frac{M(0,T_p)\left(G(T_a,T_p)+\frac{\partial_x 01(0,T_a,T_b)}{01(0,T_a,T_b)}\right)}{\partial_{x} S^{ois}_{a,b}(0)}.
\end{equation*}
Then from the last equalities, we can approximate the convexity adjustment of a CMS rate as
\begin{align*}
&CA_{CMS}(T_a,T_b) \\ 
\approx& \alpha 01(0,T_a,T_b) \partial_{x}S_{a,b}(0,\bar{x}_0, \bar{y}({T_a}) \partial_{x}S^{ois}_{a,b}(0,\bar{x}_0, \bar{y}({T_a}) \frac{ \sigma^2(1-\exp(-2kT_a))}{2k}  \\   
=& - P_{ois}(0,T_p) \left(G(T_a,T_p)+\frac{\partial_x 01(0,T_a,T_b)}{01(0,T_a,T_b)}\right) \partial_{x}S_{a,b}(0,\bar{x}_0, \bar{y}({T_a})) \frac{S^{ois}_{a,b}(0,\bar{x}_0, \bar{y}({T_a}))}{S^{ois}_{a,b}(0)}  \frac{ \sigma^2(1-\exp(-2kT_a))}{2k}
\end{align*}
In the next figure, we can see the convexity adjustment for a CMS where the tenor for the underlying swap is 5Y using the last approximation and Monte Carlo method

\section*{Appendix}
\appendix
\renewcommand{\thesection}{\Alph{section}.\arabic{section}}
\section{Approximation of $\mathbb{E}_s^{T_p}\left(D_s x_{T_a}\right)$}
\label{expected_forward_measure_malliavin_derivative_x_t}
From (\ref{short_rate_cheyette}) is easy to show that
\begin{equation*}
x_{T_a} = \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) y_u du + \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,x_u,y_u) dW_u^{\mathbb{Q}}  
\end{equation*}
In order to get an approximation for $D_sX_{T_a}$ we must to avoid the recurrence in the Malliavin derivative of $X_{T_a}$. Follow, the ideas of Piterbarg Volume II, we can approximate $y_t$ the next way
\begin{equation*}
y_t \approx \int_{0}^{s} \exp\left(-2\int_{u}^{s} k_{u^{\prime}} du^{\prime} \right) \eta(u,x_0,y_0) du
\end{equation*}
Therefore, if we define $\bar{y}(t)= \int_{0}^{s} \exp\left(-2\int_{u}^{s} k_{u^{\prime}} du^{\prime} \right) \eta(u,x_0,y_0)$, we have that
\begin{equation*}
X_{T_a} \approx \bar{X}(T_a):=\int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{y}(u) du + \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}}  
\end{equation*}
With initial condition  $\bar{x}_{0}$ is such that $S_{a,b}(0,\bar{x}_0, \bar{y}({T_a})) = S_{a,b}(0)$ (see Piterbarg Volume II). Then we can do the next approximation for the Malliavin derivative of $X_{T_a}$
\begin{equation}\label{approximation_D_s_x_t}
D_sX_{T_a} \approx  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,\bar{x}_0,\bar{y}_{T_a})\bar{M}(s,T_a)
\end{equation}
where
\begin{equation*}
\bar{M}(s,T_a) = \exp\left(-\frac{\int_{s}^{t_0} \left(\partial_x \beta(u,T_a,\bar{x}_0,\bar{y}_{T_a})\right)^{2} du}{2} + \int_{s}^{t_0} \partial_x \beta(u,T_a,\bar{x}_0,\bar{y}_{T_a}) dW^{\mathbb{Q}}_u \right)
\end{equation*}
Now, we must remember that by Girsanov's theorem we have that 
\begin{equation*}
dW^{\mathbb{Q}^{T_p}} = dW^{\mathbb{Q}} + \nu(t,T_p) dt 
\end{equation*}
and therefore 
\begin{equation}\label{approsimation_E_s_x_t}
\mathbb{E}_s^{T_p}\left(D_s x_{T_a}\right) \approx \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,\bar{x}_0,\bar{y}_{T_a}) \exp\left(-\int_{s}^{T_a} \partial_x \beta(u,T_a,\bar{x}_0,\bar{y}_{T_a}) \nu(u,T_p) du \right)
\end{equation}

>>>>

\section{Convexity Adjustment}\label{sec:CA}
In this section, we derive the convexity adjustment for different products. The advantage of using the Malliavin calculus is that it allows us to derive a general representation formula for the convexity adjustment. In order to introduce a general idea of the method. Let define a $Z_t = f(x_t)$. Now, we suppose that $Z_t$ is martingale under the measure $\mathbb{Q}_1$ and that we want to compute $\mathbb{E}^{\mathbb{Q}_2}\left(Z_T \right)$, where $\mathbb{Q}_2$ is a measure such that $\frac{d\mathbb{Q}_2}{d\mathbb{Q}_1} = \lambda_t$.

Since the convexity adjustment is derived for the Cheyette model, it can be applied to all included models, such as the Hull-White model.

@@

dW^{\mathbb{Q}^{t_2}} = dW^{\mathbb{Q}} + \nu(t,t_2) dt. 

@@

We suppose, that we have a flow in $T_a < T_p < T_b$ with value $S_{a,b}(T_a)$. Then, the present value of this flow under the differents measure $\mathbb{Q}^{T_a}$,$\mathbb{Q}^{01(a,b)}$ and $\mathbb{Q}^{T_p}$ respectivaly is 
\begin{align}\label{cms_expedted_value}
P_{ois}(0,T_a)\mathbb{E}^{\mathbb{Q}^{T_{a}}}\left(S_{a,b}(T_a) P_{ois}(T_a,T_p) \right) &= 01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) \frac{P_{ois}(T_a,T_p)}{01(T_a,T_a,T_b) }\right) \nonumber \\
&= 01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) M(T_a,T_p)\right) \\
&=P_{ois}(0,T_p)\mathbb{E}^{\mathbb{Q}^{T_p}}\left(S_{a,b}(T_a)\right)
\end{align}
where $M(t, T_p)= \frac{P_{ois}(t,T_p) }{01(t,T_a,T_b)} $. From the definition of $S_{a,b}(t)$ and $S^{ois}_{a,b}(t)$, we have that both are martingale under the measure $\mathbb{Q}^{01(a,b)}$. Therefore, we will define the convexity adjustment for CMS the next  way
\begin{equation*}
CA_{cms}(T_0,T_p) = S_{a,b}(0) - \mathbb{E}^{\mathbb{Q}^{T_p}}\left(S_{a,b}(T_a)\right). 
\end{equation*}
We will follow the same strategy that in the last examples. From Clark-Ocone formula we have that
\begin{equation*}
S_{a,b}(T_a) = \mathbb{E}^{\mathbb{Q}^{T_p}}\left(S_{a,b}(T_a)\right) + \int_{0}^{T_a} \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s S_{a,b}(T_a)\right) dW^{T_p}_s 
\end{equation*} 
Therefore, if we take $\mathbb{E}^{01(a,b)}$ and we use the Girsanov theorem  in the last expression, we get 
\begin{equation*}
S_{a,b}(0) = \mathbb{E}^{\mathbb{Q}^{T_p}}\left(S_{a,b}(T_a)\right) + \frac{01(0,T_a,T_b)}{P_{ois}(0,T_p)} \mathbb{E}^{T_p}\left(M(T_a,T_p) \int_{0}^{T_a} \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s S_{a,b}(T_a)\right) dW^{T_p}_s \right)
\end{equation*}
Now, if we use that the Skorohod integral is the adjoint operator of the Malliavin derivative, we have that
\begin{align*}
S_{a,b}(0) &= \mathbb{E}^{\mathbb{Q}^{T_p}}\left(S_{a,b}(T_a)\right) + \frac{01(0,T_a,T_b)}{P_{ois}(0,T_p)} \mathbb{E}^{T_p}\left(\int_{0}^{T_a} D_s M(T_a,T_p) \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s S_{a,b}(T_a)\right) ds  \right) \\
&=\mathbb{E}^{\mathbb{Q}^{T_p}}\left(S_{a,b}(T_a)\right) + \frac{01(0,T_a,T_b)}{P_{ois}(0,T_p)} \mathbb{E}^{T_p}\left(\int_{0}^{T_a} \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s M(T_a,T_p)\right) \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s S_{a,b}(T_a)\right) ds  \right).
\end{align*}
Then we have the next expression for the convexity adjustment
\begin{equation*}
CA_{cms}(T_0,T_p) = \frac{01(0,T_a,T_b)}{P_{ois}(0,T_p)} \mathbb{E}^{T_p}\left(\int_{0}^{T_a} \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s M(T_a,T_p)\right) \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s S_{a,b}(T_a)\right) ds  \right).
\end{equation*}
Now, if we do a freeze of $\partial_x M(t,T_p)$ and $\partial_x S_{a,b}(t)$, then we can do the next approximation for $CA_{ois}(T_0,T_p)$
\begin{align*}
CA_{cms}(T_0,T_p) &=  \frac{01(0,T_a,T_b)}{P_{ois}(0,T_p)} \mathbb{E}^{T_p}\left(\int_{0}^{T_a} \mathbb{E}^{T_p}_s \left(\partial_x M(T_a,T_p) D_s x_{T_a}\right) \mathbb{E}^{T_p}_s \left(\partial_x S_{a,b}(T_a)D_s x_{T_a} \right) ds \right) \\
& \approx \frac{01(0,T_a,T_b)}{P_{ois}(0,T_p)} \partial_x M(T_a,T_p, x_0, y_0)  \partial_x S_{a,b}(T_a,x_0,y_0) \mathbb{E}^{\mathbb{Q}^{T_p}}\left(\int_{0}^{T_a} \left(D_s x_{T_a} \right)^{2} ds \right).
\end{align*}
Now, if we use (\ref{approximation_D_s_x_t}) we can estimate  
$
 \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(\left(D_s x_{T_a} \right)^{2}\right)
$
the next way 
\begin{align*} 
\mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(\left(D_s x_{T_a} \right)^{2}\right) &\approx \exp\left(-2 \int_{s}^{T_a}k_u du \right) \eta^{2}(s,\bar{x}_0,\bar{y}_{T_a}) \\
& \cdot \exp\left(\int_{s}^{T_a} \left(\partial_x \beta(u,T_a,\bar{x}_0,\bar{y}_{T_a})\right)^{2} - 2 \exp\left(-\int_{s}^{T_a}k_u du\right) \partial_x (\bar{\nu}(u,T_a) \bar{\nu}(u,T_p)) \right) du
\end{align*}
Therefore, we have that
\begin{align*}
CA_{cms}(T_0,T_p) &\approx 
\end{align*}

\begin{example}
In the case of a Hull-White model, we showed in the example  (\ref{example_convexity_hw_ois}) that 
$$
\eta(t,x_t, y_t) = \sigma\exp(-kt)
$$
\end{example}
Therefore (\ref{cms_adjustment}) is reduced to
\begin{equation}\label{hullwhite_cms_convexity}
01(0,T_a,T_b)  f^{\prime}(S^{ois}_{a,b}(T_a)) \partial_{x}S_{a,b}(0,\bar{x}_0, \bar{y}({T_a}) \partial_{x}S^{ois}_{a,b}(0,\bar{x}_0, \bar{y}({T_a}) \frac{ \sigma^2(1-\exp(-2kT_a))}{2k} 
\end{equation}
A common practice in market, it is suppose that $f(x)=\alpha x + \beta$ (TSR model). We must to impose two equations in order to get $\alpha$ and $\beta$. The first equation follows straightforward from the definition of $M(t,T_p)$. Since, $M(t,T_p)$ is a $01(a,b)-$martingale we must have that
\begin{equation*}
\mathbb{E}^{01(a,b)}\left(\alpha S^{ois}_{a,b}(T_a) + \beta \right) = \frac{P_{ois}(0,T_p)}{01(0,T_a,T_b)}.
\end{equation*}
Therefore
\begin{equation*}
\beta = \frac{P_{ois}(0,T_p)}{01(0,T_a,T_b,x_0,y_0)} - \alpha S^{ois}_{a,b}(0,x_0,y_0).
\end{equation*}
Under a separable HJM dynamic we must have that
\begin{equation*}
\alpha \partial_{x} S^{ois}_{a,b}(0) = - M(0,T_p)\left(G(T_a,T_p)+\frac{\partial_x 01(0,T_a,T_b)}{01(0,T_a,T_b)}\right).
\end{equation*}
Then
\begin{equation*}
\alpha = -\frac{M(0,T_p)\left(G(T_a,T_p)+\frac{\partial_x 01(0,T_a,T_b)}{01(0,T_a,T_b)}\right)}{\partial_{x} S^{ois}_{a,b}(0)}.
\end{equation*}
Then from the last equalities, we can approximate the convexity adjustment of a CMS rate as
\begin{align*}
&CA_{CMS}(T_a,T_b) \\ 
\approx& \alpha 01(0,T_a,T_b) \partial_{x}S_{a,b}(0,\bar{x}_0, \bar{y}({T_a}) \partial_{x}S^{ois}_{a,b}(0,\bar{x}_0, \bar{y}({T_a}) \frac{ \sigma^2(1-\exp(-2kT_a))}{2k}  \\   
=& - P_{ois}(0,T_p) \left(G(T_a,T_p)+\frac{\partial_x 01(0,T_a,T_b)}{01(0,T_a,T_b)}\right) \partial_{x}S_{a,b}(0,\bar{x}_0, \bar{y}({T_a})) \frac{S^{ois}_{a,b}(0,\bar{x}_0, \bar{y}({T_a}))}{S^{ois}_{a,b}(0)}  \frac{ \sigma^2(1-\exp(-2kT_a))}{2k}
\end{align*}
In the next figure, we can see the convexity adjustment for a CMS where the tenor for the underlying swap is 5Y using the last approximation and Monte Carlo method

\section*{Appendix}
\appendix
\renewcommand{\thesection}{\Alph{section}.\arabic{section}}
\section{Approximation of $\mathbb{E}_s^{T_p}\left(D_s x_{T_a}\right)$}
\label{expected_forward_measure_malliavin_derivative_x_t}
From (\ref{short_rate_cheyette}) is easy to show that
\begin{equation*}
x_{T_a} = \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) y_u du + \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,x_u,y_u) dW_u^{\mathbb{Q}}  
\end{equation*}
In order to get an approximation for $D_sX_{T_a}$ we must to avoid the recurrence in the Malliavin derivative of $X_{T_a}$. Follow, the ideas of Piterbarg Volume II, we can approximate $y_t$ the next way
\begin{equation*}
y_t \approx \int_{0}^{t} \exp\left(-2\int_{u}^{t} k_{u^{\prime}} du^{\prime} \right) \eta(u,x_0,y_0) du
\end{equation*}
Therefore, if we define $\bar{y}(t)= \int_{0}^{s} \exp\left(-2\int_{u}^{s} k_{u^{\prime}} du^{\prime} \right) \eta(u,x_0,y_0)$, we have that
\begin{equation*}
X_{T_a} \approx \bar{X}(T_a):= \bar{x}_0  + \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{y}(u) du + \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}}  
\end{equation*}
With initial condition  $\bar{x}_{0}$ is such that $S_{a,b}(0,\bar{x}_0, \bar{y}({T_a})) = S_{a,b}(0)$ (see Piterbarg Volume II). Now, we must remember that by Girsanov's theorem we have that 
\begin{equation*}
dW^{\mathbb{Q}^{T_p}} = dW^{\mathbb{Q}} + \bar{\nu}(t,T_p) dt 
\end{equation*}
where $\bar{\nu}(t,T_p) = \int_{t}^{T_p} \eta(s,\bar{x}_s,\bar{y}_s) ds $. Then, we have the next approximation of $\bar{x}_{T_a}$
\begin{align*}
X_{T_a} &\approx \bar{x}_0  + \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{y}_s ds - \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{\nu}(s, T_p) \eta(s,\bar{x}_s,\bar{y}_s) ds +  \\
&+ \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right) \partial_x \eta(s,\bar{x}_s,\bar{y}_s) dW_s^{\mathbb{Q}}  
\end{align*} 
Therefore, if we taj¡ke the Malliavin derivative of $\bar{X}_{T_a}$ we get
\begin{equation}\label{approximation_D_s_x_t}
D_sX_{T_a} \approx  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(s,\bar{x}_0,\bar{y}_{T_a})\bar{M}(s,T_a)
\end{equation}
where
\begin{align*}
\bar{M}(s,T_a) &= \exp\left(-\int_{s}^{T_a} \left( \frac{\left(\partial_x \beta(u,T_a,\bar{x}_0,\bar{y}_{T_a})\right)^{2}}{2} - \exp\left(-\int_{u}^{T_a}k_u du\right) \partial_x (\bar{\nu}(u,T_a) \bar{\nu}(u,T_p))\right) du \right) \\ 
&\cdot\exp\left(\int_{s}^{t_0} \partial_x \beta(u,T_a,\bar{x}_0,\bar{y}_{T_a}) dW^{\mathbb{Q}}_u \right)
\end{align*}
With $\beta(u,T_a,x,y) = \exp\left(-\int_{u}^{T_a}k_u du\right) \partial_x \eta(u,x,y)$. Therefore, if we use the last equalities, we get the next approximation of $\mathbb{E}_s^{T_p}\left(D_s x_{T_a}\right)$

\begin{equation}\label{approsimation_E_s_x_t}
\mathbb{E}_s^{T_p}\left(D_s x_{T_a}\right) \approx \eta(s,\bar{x_0},\bar{y}_{u}) \exp\left(-\int_{s}^{T_a}k_u du \right) \exp\left(-\int_{s}^{T_a} \exp\left(-\int_{u}^{T_a}k_u du\right)\partial_x (\bar{\nu}(u,T_a) \bar{\nu}(u,T_p)) du \right).
\end{equation}

\section{Approximation of $\mathbb{E}_s^{\mathbb{Q}}\left(D_s x_{T_a}\right)$}
Following the same procedure as before, we have that
\begin{equation*}
X_{T_a} \approx \bar{X}(T_a):= \bar{x}_0  + \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{y}(u) du + \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}}  
\end{equation*}
and therefore (see (\ref{approsimation_E_s_x_t}))
\begin{equation}
D_sX_{T_a} \approx  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(s,\bar{x}_0,\bar{y}_{T_a})\bar{M}(s,T_a)
\end{equation}
Now, if we take $\mathbb{E}^{\mathbb{Q}}\left(\cdot\right)$ we get
\begin{equation}\label{approsimation_spot_E_s_x_t}
\mathbb{E}^{\mathbb{Q}}_s\left(D_sX_{T_a} \right) \approx \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(s,\bar{x}_0,\bar{y}_{T_a})
\end{equation}
